### 2016-08-31 syntax.tex
making the data structure synatax more succinct

\heading{Data structures.}  We being by defining a general primitive
that produces a representation of a given multiset, and provides a
mechanism to answer a specified collection of questions about that
multiset.
%Informally, the representation should serve as a good
%approximation of the multiset, at least with respect to the allowed queries.
\begin{definition}[Data structure] \rm
Fix a non-empty set~$\univ$. A \emph{data structure} (over universe~$\univ$)
is a tuple $\setprim=(\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$ where:
\begin{itemize}
\item $\Sigma$ is the \emph{representation alphabet}.
%\jnote{Is there any reason not to simply fix this to $\{0,1\}$?}
\item $\Gamma$ is the set of possible \emph{query answers}.
%\jnote{Do we need this for any reason?}
\item $\calS$ is a set  of multisets over universe~$\univ$.
\item $\mathcal{Q}=\{q \colon \mathcal{S} \to \Gamma\}$ is a set
    of supported \emph{queries}.
\item $\Rep \colon \mathcal{S} \to \Sigma^* \times \bits^*
    \times \bits^*$ is a randomized \emph{representation
    algorithm}, taking as input $S \in \mathcal{S}$, and
    outputting a \emph{representation} $M \in \Sigma^*$,
    \emph{private side information} $\privaux \in \bits^*$, and
    \emph{public side information} $\pubaux \in \bits^*$.  We write
    $(M,\pubaux,\privaux) \getsr \Rep(S)$ as shorthand for this execution.
\item $\Qry\colon \Sigma^* \times \bits^* \times \bits^* \times \calQ \to
    \Gamma$ is a deterministic \emph{query-evaluation}
    algorithm, taking as input $M\in\Sigma^*$, $\pubaux,\privaux \in
    \bits^*$ and $q \in \calQ$, and outputting
    an \emph{answer} $a \in \Gamma$.  We write $a \gets
    \Qry(M,\pubaux,\privaux,q)$ for this execution.
\end{itemize}
\hfill\dqed
\end{definition}
%\tsnote{I implemented this change.}\tsnote{I'm now leaning towards
%having $\Rep$ output~$M$ and explicit pubic/private auxillary data.
%Pushing secrets into~$M$ makes it more difficult to capture (for
%example) the Neidermeier et al.\ attacks in our privacy notions; see
%Figure~\ref{fig:privacy}.  In those attacks, the adversary would get
%the bitarray (which one naturally thinks of as~$M$) but not the
%secret keys for the PRFs/hash functions.  You could say that the
%bitarray is put in $\aux$ and that~$M$ \emph{only} contains the
%secret keys, but this is unnatural.}
All of the data structures that
we will consider have the property that~$|M|$ does not depend on the
coins of~$\Rep$. Thus we assume that~$|M|$ depends only on~$|S|$. In
general this need not be true, but the assumption does not restrict
our syntax from capturing natural constructions (e.g., those used in
practice), and it makes it easier to state our security notions.

>>>>

\heading{Data structures.}  We being by defining a general primitive
that produces a representation of a given multiset, and provides a
mechanism to answer a specified collection of questions about that
multiset.
%Informally, the representation should serve as a good
%approximation of the multiset, at least with respect to the allowed queries.
\begin{definition}[Data structure] \rm
Fix a non-empty set~$\univ$, and a set of multisets~$\calS$ over
$\univ$. 
A \emph{data structure} (for $\calS$) is a tuple $\setprim=(\calQ,\Rep, \Qry)$ where:
\begin{itemize}
\item $\mathcal{Q}=\{q \colon \mathcal{S} \to \Gamma\}$ is a set
    of supported \emph{queries}, where $\Gamma$ is the set of query \emph{answers}.
\item $\Rep \colon \mathcal{S} \to \bits^*
    \times \bits^*$ is a randomized \emph{representation
    algorithm}, taking as input $S \in \mathcal{S}$, and
    outputting a \emph{representation} $M \in \Sigma^*$,
    \emph{private side information} $\privaux \in \bits^*$, and
    \emph{public side information} $\pubaux \in \bits^*$.  We write
    $(M,\pubaux,\privaux) \getsr \Rep(S)$ as shorthand for this execution.
\item $\Qry\colon \Sigma^* \times \bits^* \times \bits^* \times \calQ \to
    \Gamma$ is a deterministic \emph{query-evaluation}
    algorithm, taking as input $M\in\Sigma^*$, $\pubaux,\privaux \in
    \bits^*$ and $q \in \calQ$, and outputting
    an \emph{answer} $a \in \Gamma$.  We write $a \gets
    \Qry(M,\pubaux,\privaux,q)$ for this execution.
\end{itemize}
\hfill\dqed
\end{definition}
%\tsnote{I implemented this change.}\tsnote{I'm now leaning towards
%having $\Rep$ output~$M$ and explicit pubic/private auxillary data.
%Pushing secrets into~$M$ makes it more difficult to capture (for
%example) the Neidermeier et al.\ attacks in our privacy notions; see
%Figure~\ref{fig:privacy}.  In those attacks, the adversary would get
%the bitarray (which one naturally thinks of as~$M$) but not the
%secret keys for the PRFs/hash functions.  You could say that the
%bitarray is put in $\aux$ and that~$M$ \emph{only} contains the
%secret keys, but this is unnatural.}
All of the data structures that
we will consider have the property that~$|M|$ does not depend on the
coins of~$\Rep$. Thus we assume that~$|M|$ depends only on~$|S|$. In
general this need not be true, but the assumption does not restrict
our syntax from capturing natural constructions (e.g., those used in
practice), and it makes it easier to state our security notions.
